---
title: "Prices Dataset Exploration"
author: Shan Yu
date: Sys.Date()
output:
  md_document:
    variant: markdown_github
---
```{r echo=FALSE,warning=FALSE,message=FALSE,error=FALSE}
library(sugrrants)
library(tidyverse)
library(lubridate)
library(plotly)
setwd("~/Dropbox/DMC")
train <- read.csv("raw_data/train.csv", sep = "|")
prices <- read.csv("raw_data/prices.csv", sep = "|")
items <- read.csv("raw_data/items.csv", sep = "|")
Sale=read.csv("sale.csv")
```
There are no missing data in train.
```{r,warning=FALSE,message=FALSE,error=FALSE}
## no missing in training data
apply(train, 2, function(x) sum(is.na(x)))
```
There are 1134 missing data in subCategory
```{r,warning=FALSE,message=FALSE,error=FALSE}
## some missing in subCategory
apply(items, 2, function(x) sum(is.na(x)))
```
## Price Changes
123 dates in the first 4 months
```{r,warning=FALSE,message=FALSE,error=FALSE}
date <- ymd(train$date)
range(date)
unique(date) %>% length()
```
For the majority of the items, the prices are kept the same over the time. The prices tends to change more in the February (to sold out).
```{r,warning=FALSE,message=FALSE,error=FALSE}
f=function(x) length(unique(x[!is.na(x)]))
# check the price change in from 2017-10-01 to 2018-01-31
table(apply(prices[,3:125],1,f))
# check the price change in from 2017-10-01 to 2018-02-28
table(apply(prices[,3:153],1,f))
```
## Daily Price and Daily Sale
Here we explore influence of price on the daily sale (only consider each (pid size) with price change, 1473 in total). By calculate the correlation, we could find out most of them are negative correlated.
```{r,warning=FALSE,message=FALSE,error=FALSE}
ItemPrice=left_join(items,prices, by = c("pid", "size"))
PP=ItemPrice[,11:161]/ItemPrice[,5]
PP1=PP[,1:123]
Change=apply(PP1,1,f)
relation=NULL
for (iter in which(Change>1)){
  tt=which(!is.na(PP1[iter,]))
  relation=c(relation,cor(t(PP1[iter,tt]),t(Sale[iter,tt+2])))
}
# density plot of correlation
plot(density(relation),main='Correlation between daily price and daily sale')
# high negative correlated
x=1:151
id=649
daily_sale=t(Sale[id,-(1:2)])
daily_price=t(PP[id,])*max(daily_sale)
data=data.frame(x,daily_sale,daily_price)
colnames(data)=c('x','daily_sale','daily_price')
p <- plot_ly(data, x=~x, y=~daily_sale,name='Sale',type='scatter',mode='lines+markers') %>%
  add_trace(y=~daily_price, name='price', mode='lines+markers')
p  
# midden negative correlated
x=1:151
id=887
daily_sale=t(Sale[id,-(1:2)])
daily_price=t(PP[id,])*max(daily_sale)
data=data.frame(x,daily_sale,daily_price)
colnames(data)=c('x','daily_sale','daily_price')
p <- plot_ly(data, x=~x, y=~daily_sale,name='Sale',type='scatter',mode='lines+markers') %>%
  add_trace(y=~daily_price, name='price', mode='lines+markers')
p  
# low negative correlated
x=1:151
id=8942
daily_sale=t(Sale[id,-(1:2)])
daily_price=t(PP[id,])*max(daily_sale)
data=data.frame(x,daily_sale,daily_price)
colnames(data)=c('x','daily_sale','daily_price')
p <- plot_ly(data, x=~x, y=~daily_sale,name='Sale',type='scatter',mode='lines+markers') %>%
  add_trace(y=~daily_price, name='price', mode='lines+markers')
p 
# positive correlated
x=1:151
id=6696
daily_sale=t(Sale[id,-(1:2)])
daily_price=t(PP[id,])*max(daily_sale)
data=data.frame(x,daily_sale,daily_price)
colnames(data)=c('x','daily_sale','daily_price')
p <- plot_ly(data, x=~x, y=~daily_sale,name='Sale',type='scatter',mode='lines+markers') %>%
  add_trace(y=~daily_price, name='price', mode='lines+markers')
p 
```
# Stock size
Notice: there are 7616 (pid size) only having one stock.
```{r,warning=FALSE,message=FALSE,error=FALSE}
plot(table(items$stock),xlab='frequency')
```
