---
title: "DMC1"
author: "Hao Sun"
output:
  md_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = 'figures/')
```


```{r include=FALSE,results='hide'}
#read data
library(tidyverse)
library(sugrrants)
library(lubridate)
library(pander)
items<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\items.csv",head=T,sep="|")
#  pid  size  color  brand  rrp  mainCategory  category  subCategory  stock  releaseDate
train<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\train.csv",head=T,sep="|")
#  date  pid  size  units
prices<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\prices.csv",head=T,sep="|")
#  pid  size  date(from 2017/10/1 to 2018/2/28)

```

```{r}
apply(train, 2, function(x) sum(is.na(x)))
apply(items, 2, function(x) sum(is.na(x)))


```
The items has missing data in subCategory

```{r}
table(items$mainCategory)
table(items$category)
table(items$subCategory)
table(items$category,items$mainCategory) %>% pander
table(items$subCategory,items$mainCategory)
table(items$subCategory,items$category)
items %>% filter(mainCategory==15) %>% select(subCategory) %>% is.na() %>% sum()
table(items$mainCategory,items$brand)

```
From the tables above, there are 3 main categories and each of them has its unique categories. All the products whose mainCategory are 15 do not have subCategory. Besides, in each maincategory, different categories have different subcategories. 



```{r}
train$date <- ymd(train$date)
range(train$date)
range(train$date) %>% diff   
unique(train$date) %>% length()
```

```{r}
## about 85% of the items released before 2017-10-01
items$releaseDate <- ymd(items$releaseDate)   
mean(items$releaseDate == ymd("2017-10-01"))
items_dif<-as.vector(items$releaseDate-min(items$releaseDate))
hist(items_dif,breaks=25)
```

```{r}
unique(items$pid) %>%length()
items %>% group_by(pid) %>%
  summarise(ndate = unique(releaseDate) %>% length) %>%
  select(ndate) %>% table()
```
Therefore, we know that each product had only one release date for all sizes. 

```{r} 
table(items$size) %>% names()
table(items$color)
table(items$brand)
table(items$rrp)
``` 

```{r}
items%>%filter(size=="") %>% pander
```
These 9 items do not have a size and they all belong to mainCategory 1, category 2 and subcategory 27. By checking the table above, we find that these items are the only items that belong to subCategory 27. 

#############################
Study Price

```{r}
prices2<-read.csv(file="D:\\PhD\\Project\\DMC\\prices2.csv",header=T)
price_dif<-apply(prices2[,-c(1,2,3)],MARGIN = 1,diff)  #difference between two adjacent days
find_price_dif<-function(x) {
  return(sum(x!=0)!=0)
}
price_dif<-t(price_dif)
sum(apply(price_dif,MARGIN = 1,find_price_dif))  
```
We find that there are only 1866 items among 12824 items that had price change from 2017-10-1 to 2018-1-31. 


####2018/4/14
```{r}
n_brand<-table(items$brand)
brand_stock<-as.data.frame(t(table(items$brand,items$stock)))
brand_stock%>%spread(key=Var2,value=Freq) ->brand_stock
order1<-order(n_brand,decreasing = T)                        #order
brand_stock<-brand_stock[,c(1,order1+1)]
row0<-c(0,n_brand[order1])
brand_stock<-rbind(row0,brand_stock)                       #first line is the total items 
```

```{r}
brand_releaseDate<-table(items$brand,items$releaseDate=="2017-10-1")
brand_releaseDate<-brand_releaseDate[order1,]
```

```{r}
brand_changePrice<-(table(items$brand,apply(
  price_dif,MARGIN = 1,find_price_dif)))[order1,]
brand_changePrice<-cbind(brand_changePrice,rate=
                           brand_changePrice[,2]/apply(brand_changePrice,1,sum))
```

```{r}
subCategory_changePrice<-(table(items$subCategory,apply(
  price_dif,MARGIN = 1,find_price_dif)))
subCategory_changePrice<-cbind(subCategory_changePrice,rate=
                           subCategory_changePrice[,2]/apply(subCategory_changePrice,1,sum))
subCategory_changePrice<-subCategory_changePrice[order(subCategory_changePrice[,3],decreasing = T),]
```

```{r}
category_changePrice<-table(items$category,apply(
  price_dif,MARGIN = 1,find_price_dif))
category_changePrice<-cbind(category_changePrice,rate=
                           category_changePrice[,2]/apply(category_changePrice,1,sum))
category_changePrice<-category_changePrice[order(category_changePrice[,3],decreasing = T),]
```

```{r}
price_dif2<-price_dif[order(prices$pid),]/items$rrp
price_diftotal<-as.vector(apply(price_dif2,MARGIN=2,mean,na.rm=T))
date=ymd(strtrim(seq(ISOdate(2017,10,2), ISOdate(2018,2,28), "DSTday"),10))
d_pricediftotal<-data.frame(date,price_diftotal)
ggplot(data=d_pricediftotal,aes(x=date,y=price_diftotal))+geom_line()
```
The values in this plot are all price change average over rrp, and the formula is $\frac{1}{N}\sum^N_{i=1}\frac{Price_{ i}-Price_{i-1}}{rrp}$. From this figure above, we can find that the price in Jan and Feb,2018 had large change and the change was very frequent. Another big change happend during the Black Friday in Nov 2017. 
```{r}
ggplot(data=d_pricediftotal[122:150,],aes(x=date,y=price_diftotal))+geom_line()
```
Here is the price average change over rrp plot in Feb 2018. We can see that at the beginning the price rose a lot and on 25th Feb, the price declined a lot. Probabily the price were affected by Winter Olymptic Game and another festival called Fasching on 27th Feb. The Valentine's Day had some impact on the price, but not very much. 

```{r}
date2=ymd(strtrim(seq(ISOdate(2017,10,1), ISOdate(2018,2,28), "DSTday"),10))
prices2<-prices[order(prices$pid),]   #change the pID order to be the same as items 
prices_average<-data.frame(category=items$category,prices2[,-c(1,2)]/items$rrp)
prices_totalaverage<-data.frame(date=date2,prices_totalaverage=
                                  as.vector(apply(prices_average[,-1],MARGIN=2,FUN=mean,na.rm=T)))
ggplot(prices_totalaverage,aes(x=date,y=prices_totalaverage))+geom_line()


```
Here is plot shows the average price over rrp for all items. We can find the downtrend and the price got the lowest on 25th Feb and then rose up a lot. 
```{r}
prices_average$category<-factor(prices_average$category)
prices_average%>% gather(date,value,-category)%>% group_by(category,date) %>% summarise_at(vars(value), funs(mean(., na.rm=T))) %>% ungroup %>% as.data.frame() ->prices_average2
prices_average2$date<-rep(date2,each1=10)
ggplot(data=prices_average2,aes(x=date,y=value,col=as.factor(category)))+
  geom_line()+facet_wrap(~category,ncol=3)+theme(legend.position='none')
```
we can find that different category has different discount. The category 7, 16, 24, 33 have big discount where 16, 24, 33 belong to mainCategory 15 and 7 belongs to mainCategory 1. Category 2, 10, 18, 36, 37 have small discount where 10, 18, 36, 37 belong to mainCategory 9 and 37 and 2 belongs to mainCategory 1. 

```{r}
table(items$category,items$mainCategory) %>% pander
ggplot(data=prices_average2,aes(x=date,y=value,col=as.factor(category)))+
  geom_line()+facet_wrap(~category,scales="free",ncol=3)+theme(legend.position='none')
```



