---
title: "DMC1"
author: "Hao Sun"
output:
  md_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE,results='hide'}
#read data
library(tidyverse)
library(sugrrants)
library(lubridate)
library(pander)
items<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\items.csv",head=T,sep="|")
#  pid  size  color  brand  rrp  mainCategory  category  subCategory  stock  releaseDate
train<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\train.csv",head=T,sep="|")
#  date  pid  size  units
prices<-read.csv(file="D:\\PhD\\Project\\DMC\\raw_data\\prices.csv",head=T,sep="|")
#  pid  size  date(from 2017/10/1 to 2018/2/28)



```

```{r}
apply(train, 2, function(x) sum(is.na(x)))
apply(items, 2, function(x) sum(is.na(x)))


```
The items has missing data in subCategory

```{r}
table(items$mainCategory)
table(items$category)
table(items$subCategory)
table(items$category,items$mainCategory) %>% pander
table(items$subCategory,items$mainCategory)
table(items$subCategory,items$category)
items %>% filter(mainCategory==15) %>% select(subCategory) %>% is.na() %>% sum()
table(items$mainCategory,items$brand)

```
From the tables above, there are 3 main categories and each of them has its unique categories. All the products whose mainCategory are 15 do not have subCategory. Besides, in each maincategory, different categories have different subcategories. 



```{r}
train$date <- ymd(train$date)
range(train$date)
range(train$date) %>% diff   
unique(train$date) %>% length()
```

```{r}
## about 85% of the items released before 2017-10-01
items$releaseDate <- ymd(items$releaseDate)   
mean(items$releaseDate == ymd("2017-10-01"))
items_dif<-as.vector(items$releaseDate-min(items$releaseDate))
hist(items_dif,breaks=25)
```

```{r}
unique(items$pid) %>%length()
items %>% group_by(pid) %>%
  summarise(ndate = unique(releaseDate) %>% length) %>%
  select(ndate) %>% table()
```
Therefore, we know that each product had only one release date for all sizes. 

```{r} 
table(items$size) %>% names()
table(items$color)
table(items$brand)
table(items$rrp)
``` 

```{r}
items%>%filter(size=="") %>% pander
```
These 9 items do not have a size and they all belong to mainCategory 1, category 2 and subcategory 27. By checking the table above, we find that these items are the only items that belong to subCategory 27. 

```{r}
main_vs_size<-table(items$size,items$mainCategory)
write.csv(main_vs_size,file="D:\\PhD\\Project\\DMC\\main_vs_size.csv")
c_vs_size<-table(items$size,items$category)
write.csv(c_vs_size,file="D:\\PhD\\Project\\DMC\\c_vs_size.csv")
```

